### 2025-02-21 project2/nnMetamodels.tex
new

Let $L_1,L_2,\ldots,L_M$ be $M$ independent and identically distributed (i.i.d.) simulated losses of $L$ and let $L_{(1)}\leq L_{(2)}\leq \ldots\leq L_{(M)}$ be the ordered losses.
For a given confidence level $\alpha$ (assume that $\alpha M$ is an integer for simplicity), $\alpha$-VaR can be estimated by the sample quantile $\widehat{\VaR}_\alpha = L_{(\alpha M)}$. Also, $\alpha$-CVaR can be estimated by
\begin{equation} \label{eq2:cvar-hat}
    \widehat{\CVaR}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}L_{(i)} = \frac{1}{(1-\alpha)M} \sum_{i \in \tail_{(1-\alpha )M}}L_{i}.
\end{equation}
Equation \eqref{eq2:cvar-hat} is the same as \eqref{eq1:cvar-hat} except that we define a \textit{true tail scenario set} of size $k$ as $\tail_{k} = \{i: L_i > L_{(M-k)}\}$.
In this study, the loss random variable of interest is the hedging error for VA.

@@

\begin{algorithm}
\caption{Two-Stage Metamodeling Nested Simulation Procedure for Estimating CVaR}
\begin{algorithmic}[1] \label{alg2:twoStageProcedure}
    \STATE \textbf{Train a neural network metamodel using simulation data:}
    \begin{enumerate} [label=\alph*., itemsep=0pt, parsep=0pt, topsep=0pt]
        \item Use a fraction of the total simulation budget to run Steps 1, 2, and 3 in the standard procedure, i.e., Algorithm~\ref{alg2:standardProcedure}, with the same number of outer scenarios, $M$, but a much smaller number of inner replications, $N' \ll N$, in each scenario. 
        Obtain $M$ simulated samples (feature-label pairs), $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$. 
        Note that $N'$ may be much smaller than $N$, so $\Lhat_i$ are expected to have larger variance.
        \item Use the simulated data, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$ to train a supervised learning model. 
        It is standard practice in supervised learning research to transform the stock prices $\bS^{(i)}$ to returns $\mathbf{X}^{(i)}$,
        \begin{equation} \label{eq2:return}
        \mathbf{X}^{(i)} = \left(\frac{S_1^{(i)} - S_0}{S_0}, \frac{S_2^{(i)} - S_1^{(i)}}{S_1^{(i)}}, \ldots, \frac{S_T^{(i)} - S_{T-1}^{(i)}}{S_{T-1}^{(i)}}\right)
        \end{equation}
        and use $\mathbf{X}^{(i)}$ as features instead of the stock prices $\bS^{(i)}$.
        Refer to the trained model as a metamodel and denote it by $\Lhat^{PD}(\mathbf{X})$. Denote the predicted losses for the outer scenarios by $\Lhat^{PD}_i = \Lhat^{PD}(\mathbf{X}^{(i)})$, $i=1,\ldots,M$.
        \item Sort the predicted losses $\Lhat^{PD}_{(1)}\leq \Lhat^{PD}_{(2)} \leq \cdots\leq \Lhat^{PD}_{(M)}$ to identify a predicted tail scenario set, $\widehat{\tail}_{m}^{PD}$, associated with the largest predicted losses. The number of predicted tail scenarios, $m$, is a user's choice.
    \end{enumerate}
    \STATE \textbf{Concentrate simulation on predicted tail scenarios:}
    \begin{enumerate} [label=\alph*., itemsep=0pt, parsep=0pt, topsep=0pt]
        \item Run Steps 2 and 3 of Algorithm~\ref{alg2:standardProcedure} with the same number of inner replications, $N$, but only on the predicted tail scenarios, i.e., scenarios in $\widehat{\tail}_{m}^{PD}$. Denote the standard procedure's estimated losses and sorted losses by $\Lhat^{ML}_i$ and $\Lhat^{ML}_{(i)}$, respectively, $i=1,\ldots,m$.
        \item Estimate the $\alpha$-CVaR of $L$ by 
        $$\widehat{\CVaR}^{ML}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{ML} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha )M}^{ML}}\Lhat_{i}^{ML},$$ 
        where $\widehat{\tail}_{k}^{ML}$ denotes a predicted tail scenario set associated with the largest $k$ estimated losses.
    \end{enumerate}
\end{algorithmic}
\end{algorithm}

@@

We conduct a series of simulation experiments to 
\begin{enumerate}
    \item demonstrate the efficiency of the proposed metamodeling procedures, and
    \item examine the error tolerance to noisy training data in deep learning models.
\end{enumerate}
The problem settings in our experiments are identical to those in~\cite{dang2020efficient}.
We consider estimating the $95\%$ CVaR of the hedging loss of a GMWB contract, which is one of the most complex VA contracts in the market.
The VA contracts have a 20-year maturity and are delta-hedged with monthly rebalancing, i.e., $T=240$ rebalancing periods.
The gross and net management fees are $\eta_g = 0.2\%$ and $\eta_n=0.1\%$, respectively.
The withdrawal rate for GMWB is $0.375\%$ per month.
To make our examples more realistic, the VAs are also subject to a dynamic lapse model with the following key features~\citep{naic2021}:
\begin{enumerate}
    \item When a policyholder lapses, both the fund value ($F$) and guarantee value ($G$) are reduced proportionally.
    \item The monthly lapse rate from time $t$ to $t + 1$, denoted as ${}_{\frac{1}{12}}q^l_{x+\frac{t}{12}}$, is given by:
    \begin{equation}
        {}_{\frac{1}{12}}q^l_{x+\frac{t}{12}} = \min\left\{1, \max\left\{0.5, 1 - 1.25 \times \left(\frac{G_t}{F_t} - 1.1\right)\right\} \times {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}\right\}
    \end{equation}
    where ${}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}$ is a base monthly mortality rate for a policyholder aged $x + \frac{t}{12}$ at month $t$, and the base monthly lapse rate is defined as:
    \begin{equation}
        {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}} = 
        \begin{cases}
            0.00417 & \text{if } t < 84 \\
            0.00833 & \text{if } t \geq 84
        \end{cases}
    \end{equation}
\end{enumerate}

@@

\begin{table}[ht!]
    \small
    \centering
    \begin{tabular}{lccccc}
        \toprule
        \textbf{Model}      & \textbf{$N$}         & \textbf{Training error}                & \textbf{Test error}               & \textbf{True error}\\
        \midrule
        LSTM                & $100$                & $0.075 (\pm4.5\times 10^{-3})$         & $0.079(\pm5.4\times 10^{-3})$     & $0.063 (\pm4.4\times 10^{-3})$ \\ 
        High-capacity LSTM  & $100$                & $0.068 (\pm3.6\times 10^{-3})$         & $0.102(\pm6.1\times 10^{-2})$     & $0.060 (\pm3.6\times 10^{-3})$ \\
        Average Difference  & $100$                & $-0.007$                               & $0.023$                           & $-0.003$ \\
        \hline
        LSTM                & $10$                 & $0.195 (\pm1.1\times 10^{-3})$         & $0.193(\pm1.7\times 10^{-3})$     & $0.070 (\pm9.1\times 10^{-4})$ \\
        High-capacity LSTM  & $10$                 & $0.157 (\pm2.0\times 10^{-3})$         & $0.199(\pm1.9\times 10^{-3})$     & $0.065 (\pm1.9\times 10^{-3})$ \\
        Average Difference  & $10$                 & $-0.038$                               & $0.006$                           & $-0.005$ \\
        \hline
        LSTM                & $1$                  & $1.366 (\pm8.6\times 10^{-3})$         & $0.781(\pm6.0\times 10^{-3})$     & $0.129 (\pm5.0\times 10^{-3})$ \\
        High-capacity LSTM  & $1$                  & $1.354 (\pm2.7\times 10^{-2})$         & $0.795(\pm8.3\times10^{-2})$      & $0.149 (\pm2.7\times 10^{-2})$ \\
        Average Difference  & $1$                  & $-0.012$                               & $0.014$                           & \textcolor{red}{$0.020$} \\
        \bottomrule
    \end{tabular}
    \caption{MSEs of LSTM metamodels.}
    \label{tab:lstm_arch}
\end{table}

>>>>

Let $L_1,L_2,\ldots,L_M$ be $M$ i.i.d. simulated losses of $L$ and let $L_{(1)}\leq L_{(2)}\leq \ldots\leq L_{(M)}$ be the ordered losses.
For a given confidence level $\alpha$ (assume that $\alpha M$ is an integer for simplicity), $\alpha$-VaR can be estimated by the sample quantile $\widehat{\VaR}_\alpha = L_{(\alpha M)}$. Also, $\alpha$-CVaR can be estimated by
\begin{equation} \label{eq2:cvar-hat}
    \widehat{\CVaR}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}L_{(i)} = \frac{1}{(1-\alpha)M} \sum_{i \in \tail_{(1-\alpha )M}}L_{i}.
\end{equation}

Equation \eqref{eq2:cvar-hat} is the same as \eqref{eq1:cvar-hat} except that we define a \textit{true tail scenario set} of size $k$ as $\tail_{k} = \{i: L_i > L_{(M-k)}\}$.
In this study, the loss random variable of interest is the hedging error for VA.

@@

\begin{algorithm}
\caption{Two-Stage Metamodeling Nested Simulation Procedure for Estimating CVaR}
\begin{algorithmic}[1] \label{alg2:twoStageProcedure}
    \STATE \textbf{Train a neural network metamodel using simulation data:}
    \begin{enumerate} [label=\alph*., itemsep=0pt, parsep=0pt, topsep=0pt]
        \item Use a fraction of the total simulation budget to run Steps 1, 2, and 3 in the standard procedure, i.e., Algorithm~\ref{alg2:standardProcedure}, with the same number of outer scenarios, $M$, but a much smaller number of inner replications, $N' \ll N$, in each scenario. 
        Obtain $M$ simulated samples (feature-label pairs), $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$. 
        Note that $N'$ may be much smaller than $N$, so $\Lhat_i$ are expected to have larger variance.
        \item Use the simulated data, $(\bS^{(i)}, \Lhat_i)$, $i=1,\ldots,M$ to train a supervised learning model. 
        It is standard practice in supervised learning research to transform the stock prices $\bS^{(i)}$ to returns $\mathbf{X}^{(i)}$,
        \begin{equation} \label{eq2:return}
        \mathbf{X}^{(i)} = \left(\frac{S_1^{(i)} - S_0}{S_0}, \frac{S_2^{(i)} - S_1^{(i)}}{S_1^{(i)}}, \ldots, \frac{S_T^{(i)} - S_{T-1}^{(i)}}{S_{T-1}^{(i)}}\right)
        \end{equation}
        and use $\mathbf{X}^{(i)}$ as features instead of the stock prices $\bS^{(i)}$.
        Refer to the trained model as a metamodel and denote it by $\Lhat^{PD}(\mathbf{X})$. Denote the predicted losses for the outer scenarios by $\Lhat^{PD}_i = \Lhat^{PD}(\mathbf{X}^{(i)})$, $i=1,\ldots,M$.
        \item Sort the predicted losses $\Lhat^{PD}_{(1)}\leq \Lhat^{PD}_{(2)} \leq \cdots\leq \Lhat^{PD}_{(M)}$ to identify a predicted tail scenario set, $\widehat{\tail}_{m}^{PD}$, associated with the largest predicted losses. The number of predicted tail scenarios, $m$, is a user's choice.
    \end{enumerate}
    \STATE \textbf{Concentrate simulation on predicted tail scenarios:}
    \begin{enumerate} [label=\alph*., itemsep=0pt, parsep=0pt, topsep=0pt]
        \item Run Steps 2 and 3 of Algorithm~\ref{alg2:standardProcedure} with the same number of inner replications, $N$, but only on the predicted tail scenarios, i.e., scenarios in $\widehat{\tail}_{m}^{PD}$. Denote the standard procedure's estimated losses and sorted losses by $\Lhat^{ML}_i$ and $\Lhat^{ML}_{(i)}$, respectively, $i=1,\ldots,m$.
        \item Estimate the $\alpha$-CVaR of $L$ by 
        $$\widehat{\CVaR}^{ML}_\alpha = \frac{1}{(1-\alpha)M} \sum_{i=\alpha M + 1}^{M}\Lhat_{(i)}^{ML} = \frac{1}{(1-\alpha)M} \sum_{i \in \widehat{\tail}_{(1-\alpha)M}^{ML}}\Lhat_{i}^{ML},$$ 
        where $\widehat{\tail}_{k}^{ML}$ denotes a predicted tail scenario set associated with the largest $k$ estimated losses.
    \end{enumerate}
\end{algorithmic}
\end{algorithm}

@@

We conduct a series of simulation experiments to 
\begin{enumerate}
    \item demonstrate the efficiency of the proposed metamodeling procedures, and
    \item examine the error tolerance to noisy training data in deep learning models.
\end{enumerate}
The problem settings in our experiments are identical to those in~\cite{dang2020efficient}.
We consider estimating the $95\%$ CVaR of the hedging loss of a GMWB contract, which is one of the most complex VA contracts in the market.
The VA contracts have a 20-year maturity and are delta-hedged with monthly rebalancing, i.e., $T=240$ rebalancing periods.
The gross and net management fees are $\eta_g = 0.2\%$ and $\eta_n=0.1\%$, respectively.
The withdrawal rate for GMWB is $0.375\%$ per month.
To make our examples more realistic, the VAs are also subject to a dynamic lapse model with the following key features~\citep{naic2021}:
\begin{enumerate}
    \item When a policyholder lapses, both the fund value ($F$) and guarantee value ($G$) are reduced proportionally.
    \item The monthly lapse rate from time $t$ to $t + 1$, denoted as ${}_{\frac{1}{12}}q^l_{x+\frac{t}{12}}$, is given by:
    \begin{equation}
        {}_{\frac{1}{12}}q^l_{x+\frac{t}{12}} = \min\left\{1, \max\left\{0.5, 1 - 1.25 \times \left(\frac{G_t}{F_t} - 1.1\right)\right\} \times {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}\right\}
    \end{equation}
    where ${}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}}$ is a base monthly mortality rate for a policyholder aged $x + \frac{t}{12}$ at month $t$, and the base monthly lapse rate is defined as:
    \begin{equation}
        {}_{\frac{1}{12}}q^{base}_{x+\frac{t}{12}} = 
        \begin{cases}
            0.00417 & \text{if } t < 84, \\
            0.00833 & \text{if } t \geq 84.
        \end{cases}
    \end{equation}
\end{enumerate}

@@

\begin{table}[ht!]
    \small
    \centering
    \begin{tabular}{lccccc}
        \toprule
        \textbf{Model}      & \textbf{$N$}         & \textbf{Training error}                & \textbf{Test error}               & \textbf{True error}\\
        \midrule
        LSTM                & $\num{100}$                & $0.075 (\pm4.5\times 10^{-3})$         & $0.079(\pm5.4\times 10^{-3})$     & $0.063 (\pm4.4\times 10^{-3})$ \\ 
        High-capacity LSTM  & $\num{100}$                & $0.068 (\pm3.6\times 10^{-3})$         & $0.102(\pm6.1\times 10^{-2})$     & $0.060 (\pm3.6\times 10^{-3})$ \\
        Average Difference  & $\num{100}$                & $-0.007$                               & $0.023$                           & $-0.003$ \\
        \hline
        LSTM                & $\num{10}$                 & $0.195 (\pm1.1\times 10^{-3})$         & $0.193(\pm1.7\times 10^{-3})$     & $0.070 (\pm9.1\times 10^{-4})$ \\
        High-capacity LSTM  & $\num{10}$                 & $0.157 (\pm2.0\times 10^{-3})$         & $0.199(\pm1.9\times 10^{-3})$     & $0.065 (\pm1.9\times 10^{-3})$ \\
        Average Difference  & $\num{10}$                 & $-0.038$                               & $0.006$                           & $-0.005$ \\
        \hline
        LSTM                & $\num{1}$                  & $1.366 (\pm8.6\times 10^{-3})$         & $0.781(\pm6.0\times 10^{-3})$     & $0.129 (\pm5.0\times 10^{-3})$ \\
        High-capacity LSTM  & $\num{1}$                  & $1.354 (\pm2.7\times 10^{-2})$         & $0.795(\pm8.3\times10^{-2})$      & $0.149 (\pm2.7\times 10^{-2})$ \\
        Average Difference  & $\num{1}$                  & $-0.012$                               & $0.014$                           & \textcolor{red}{$0.020$} \\
        \bottomrule
    \end{tabular}
    \caption{MSEs of LSTM metamodels.}
    \label{tab:lstm_arch}
\end{table}

### 2025-02-21 project3/draft.tex
new

A typical TL framework for supervised learning consists of the following:
\begin{itemize}
    \item   \textbf{source domain}: $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(\mathbf{X})\}$
    \item   \textbf{source task}: $\mathcal{T}_{\text{So}} = \{\mathcal{Y}_{\text{So}}, f_{\text{So}}(\cdot)\}$
    \item   \textbf{target domain}: $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(\cdot)\}$
    \item   \textbf{target task}: $\mathcal{T}_{\text{Ta}} = \{\mathcal{Y}_{\text{Ta}}, f_{\text{Ta}}(\cdot)\}$
\end{itemize}
where $\mathcal{X}_{\text{So}}$ and $\mathcal{X}_{\text{Ta}}$ include input features derived from the outer simulation of two different VA contracts or market conditions, and $F_{\text{So}}$ and $F_{\text{Ta}}$ are the marginal probability distributions of the source and target domains, respectively.
Hence, the source domain and task are related to one VA contract for a certain market condition, while the target domain and task are related to new VA contracts and market conditions for which we don't have the simulation budget to run the standard nested simulation procedure extensively.
In our numerical experiments, the dataset is generated by running the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} for a large number of VA contracts.
The input features $\mathbf{X}$ are the return vectors from Equation~\eqref{eq2:return}, and the output labels $L$ are the contract losses for different outer scenarios.
The stock price vector $\mathbf{S}$ is not crucial for the discussion of this chapter and is omitted since it can be immediately recovered from $\mathbf{X}$ and the initial stock price $S_0$.
We keep the number of features to be $\num{240}$ for both source and target domains as in Section~\ref{sec2:numerical}.
The predictive function $f_{\text{So}}$ and $f_{\text{Ta}}$ are trained to estimate outputs $L_{\text{So}}$ and $L_{\text{Ta}}$, i.e., approximating the inner simulations under the source and target tasks, respectively.
TL seeks to improve the learning of the target predictive function $f_{\text{Ta}}(\cdot)$ in $\mathcal{D}_{\text{Ta}}$ by leveraging the previous training on $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$, particularly when $\mathcal{D}_{\text{So}} \neq \mathcal{D}_{\text{Ta}}$ or $\mathcal{T}_{\text{So}} \neq \mathcal{T}_{\text{Ta}}$.
In Chapter~\ref{chap:project2}, we have $\mathcal{D}_{\text{So}} = \mathcal{D}_{\text{Ta}}$ and $\mathcal{T}_{\text{So}} = \mathcal{T}_{\text{Ta}}$.

@@

    \STATE Train a LSTM metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
    \begin{equation}
        \theta_{\text{So}} = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2
    \end{equation}

    \STATE Initialize the target metamodel parameters $\theta_{\text{Ta}}$ using the pre-trained metamodel parameters:
    \[
    \theta_{\text{Ta}} \gets \theta_{\text{So}}
    \]

    \STATE Fine-tune the entire LSTM model $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate $\alpha_{\text{Ta}}$:
    \begin{equation}
        \theta_{\text{Ta}} = \min_{\theta} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta) - L_{\text{Ta}}^{(i)} \right)^2
    \end{equation}

    \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task
\end{algorithmic}
\end{algorithm}

@@

        \STATE Train LSTM model $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
        \begin{equation}
            \theta_{\text{So}} = [\theta_0, \theta_1] = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2
        \end{equation}

        \STATE Initialize the target model parameters $\theta_{\text{Ta}} = [\theta_0, \theta_1]$ using the pre-trained source model parameters $\theta_{\text{So}}$:
        \[
        \theta_{\text{Ta}} \gets \theta_{\text{So}} = [\theta_0, \theta_1]
        \]

@@

        \STATE Fine-tune the trainable layers $\theta_1$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using Algorithm~\ref{alg3:fineTuning}:
        \begin{equation}
            \theta_{\text{Ta}} = \min_{\theta_1} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; [\theta_0, \theta_1]) - L_{\text{Ta}}^{(i)} \right)^2
        \end{equation}

        \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; [\theta_0, \theta_1])$ for the target task
    \end{algorithmic}
    \end{algorithm}

@@

\begin{equation} 
    \min_{\theta_0, \theta_1, \dots, \theta_K} = \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_1, \dots, \theta_K) - L_k^{(i)} \right)^2,
\end{equation}

where MSE loss function is used as the error metric, and $f_i(\cdot; \theta_0, \theta_1, \dots, \theta_K)$ is the output of the network for task $k$.
In essence, multi-task learning uses a multi-head architecture, where each task has its own output head, but the shared LSTM layers learn a common representation across tasks.
Transfer occurs through the shared LSTM layers $\theta_0$. 
These layers learn representations of temporal patterns and dependencies common to all tasks, effectively \textbf{pooling} information from multiple simulation schemes. 
The task-specific fully connected layers $[\theta_1, \dots, \theta_K]$ allow each task to capture unique characteristics not shared with other tasks.

@@

        \STATE Train the multi-head LSTM metamodel on all $K$ tasks simultaneously by minimizing the multi-task loss function:
        \begin{equation} \label{eq3:multiTaskLoss}
            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
        \end{equation}

@@

        \STATE \textbf{Output:} Trained multi-task LSTM metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks
    \end{algorithmic}
\end{algorithm}

@@

        \STATE Train the multi-task LSTM metamodel on all $K$ tasks simultaneously:
        \begin{equation}
            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2
        \end{equation}

@@

        \STATE Fine-tune only $\theta_{\text{Ta}}$ on the new target dataset $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate $\alpha_{\text{Ta}}$:
        \begin{equation}
            \min_{\theta_{\text{Ta}}} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta_0, \theta_{\text{Ta}}) - L_{\text{Ta}}^{(i)} \right)^2
        \end{equation}

@@

\begin{figure}[ht!]
    \includegraphics[width=\textwidth]{./project3/tikz/mtl.pdf}
    \caption{Multi-task Learning Framework for VA Contracts}
    \label{fig3:mtl}
\end{figure}

>>>>

A typical TL framework for supervised learning consists of the following:
\begin{itemize}
    \item   \textbf{source domain}: $\mathcal{D}_{\text{So}} = \{\mathcal{X}_{\text{So}}, F_{\text{So}}(\mathbf{X})\}$,
    \item   \textbf{source task}: $\mathcal{T}_{\text{So}} = \{\mathcal{Y}_{\text{So}}, f_{\text{So}}(\cdot)\}$,
    \item   \textbf{target domain}: $\mathcal{D}_{\text{Ta}} = \{\mathcal{X}_{\text{Ta}}, F_{\text{Ta}}(\cdot)\}$,
    \item   \textbf{target task}: $\mathcal{T}_{\text{Ta}} = \{\mathcal{Y}_{\text{Ta}}, f_{\text{Ta}}(\cdot)\}$,
\end{itemize}
where $\mathcal{X}_{\text{So}}$ and $\mathcal{X}_{\text{Ta}}$ include input features derived from the outer simulation of two different VA contracts or market conditions, and $F_{\text{So}}$ and $F_{\text{Ta}}$ are the marginal probability distributions of the source and target domains, respectively.
Hence, the source domain and task are related to one VA contract for a certain market condition, while the target domain and task are related to new VA contracts and market conditions for which we don't have the simulation budget to run the standard nested simulation procedure extensively.
In our numerical experiments, the dataset is generated by running the standard nested simulation procedure in Algorithm~\ref{alg2:standardProcedure} for a large number of VA contracts.
The input features $\mathbf{X}$ are the return vectors from Equation~\eqref{eq2:return}, and the output labels $L$ are the contract losses for different outer scenarios.
The stock price vector $\mathbf{S}$ is not crucial for the discussion of this chapter and is omitted since it can be immediately recovered from $\mathbf{X}$ and the initial stock price $S_0$.
We keep the number of features to be $\num{240}$ for both source and target domains as in Section~\ref{sec2:numerical}.
The predictive function $f_{\text{So}}$ and $f_{\text{Ta}}$ are trained to estimate outputs $L_{\text{So}}$ and $L_{\text{Ta}}$, i.e., approximating the inner simulations under the source and target tasks, respectively.
TL seeks to improve the learning of the target predictive function $f_{\text{Ta}}(\cdot)$ in $\mathcal{D}_{\text{Ta}}$ by leveraging the previous training on $\mathcal{D}_{\text{So}}$ and $f_{\text{So}}(\cdot)$, particularly when $\mathcal{D}_{\text{So}} \neq \mathcal{D}_{\text{Ta}}$ or $\mathcal{T}_{\text{So}} \neq \mathcal{T}_{\text{Ta}}$.
In Chapter~\ref{chap:project2}, we have $\mathcal{D}_{\text{So}} = \mathcal{D}_{\text{Ta}}$ and $\mathcal{T}_{\text{So}} = \mathcal{T}_{\text{Ta}}$.

@@

    \STATE Train a LSTM metamodel $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
    \begin{equation}
        \theta_{\text{So}} = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2.
    \end{equation}

    \STATE Initialize the target metamodel parameters $\theta_{\text{Ta}}$ using the pre-trained metamodel parameters:
    \[
    \theta_{\text{Ta}} \gets \theta_{\text{So}}.
    \]

    \STATE Fine-tune the entire LSTM model $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate $\alpha_{\text{Ta}}$:
    \begin{equation}
        \theta_{\text{Ta}} = \min_{\theta} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta) - L_{\text{Ta}}^{(i)} \right)^2.
    \end{equation}

    \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; \theta_{\text{Ta}})$ for the target task.
\end{algorithmic}
\end{algorithm}

@@

        \STATE Train LSTM model $f_{\text{So}}(\cdot; \theta_{\text{So}})$ on $\mathcal{D}_{\text{So}}$:
        \begin{equation}
            \theta_{\text{So}} = [\theta_0, \theta_1] = \min_{\theta} \frac{1}{M_{\text{So}}} \sum_{i=1}^{M_{\text{So}}} \left( f_{\text{So}}(X_{\text{So}}^{(i)}; \theta) - L_{\text{So}}^{(i)} \right)^2.
        \end{equation}

        \STATE Initialize the target model parameters $\theta_{\text{Ta}} = [\theta_0, \theta_1]$ using the pre-trained source model parameters $\theta_{\text{So}}$:
        \[
        \theta_{\text{Ta}} \gets \theta_{\text{So}} = [\theta_0, \theta_1].
        \]

@@

        \STATE Fine-tune the trainable layers $\theta_1$ on the target dataset $\mathcal{D}_{\text{Ta}}$ using Algorithm~\ref{alg3:fineTuning}:
        \begin{equation}
            \theta_{\text{Ta}} = \min_{\theta_1} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; [\theta_0, \theta_1]) - L_{\text{Ta}}^{(i)} \right)^2.
        \end{equation}

        \STATE \textbf{Output:} Final adapted LSTM metamodel $f_{\text{Ta}}(\cdot; [\theta_0, \theta_1])$ for the target task.
    \end{algorithmic}
    \end{algorithm}

@@

\begin{equation} 
    \min_{\theta_0, \theta_1, \dots, \theta_K} = \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_1, \dots, \theta_K) - L_k^{(i)} \right)^2,
\end{equation}
where MSE loss function is used as the error metric, and $f_i(\cdot; \theta_0, \theta_1, \dots, \theta_K)$ is the output of the network for task $k$.
In essence, multi-task learning uses a multi-head architecture, where each task has its own output head, but the shared LSTM layers learn a common representation across tasks.
Transfer occurs through the shared LSTM layers $\theta_0$. 
These layers learn representations of temporal patterns and dependencies common to all tasks, effectively \textbf{pooling} information from multiple simulation schemes. 
The task-specific fully connected layers $[\theta_1, \dots, \theta_K]$ allow each task to capture unique characteristics not shared with other tasks.

@@

        \STATE Train the multi-head LSTM metamodel on all $K$ tasks simultaneously by minimizing the multi-task loss function:
        \begin{equation} \label{eq3:multiTaskLoss}
            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2.
        \end{equation}

@@

        \STATE \textbf{Output:} Trained multi-task LSTM metamodel $f(\cdot; \theta_0, \{\theta_k\}_{k=1}^K)$ for all $K$ tasks.
    \end{algorithmic}
\end{algorithm}

@@

        \STATE Train the multi-task LSTM metamodel on all $K$ tasks simultaneously:
        \begin{equation}
            \min_{\theta_0, \{\theta_k\}_{k=1}^K} \sum_{k=1}^K \frac{1}{M_k} \sum_{i=1}^{M_k} \left( f_i(X_k^{(i)}; \theta_0, \theta_k) - L_k^{(i)} \right)^2.
        \end{equation}

@@

        \STATE Fine-tune only $\theta_{\text{Ta}}$ on the new target dataset $\mathcal{D}_{\text{Ta}}$ using a smaller learning rate $\alpha_{\text{Ta}}$:
        \begin{equation}
            \min_{\theta_{\text{Ta}}} \frac{1}{M_{\text{Ta}}} \sum_{i=1}^{M_{\text{Ta}}} \left( f_{\text{Ta}}(X_{\text{Ta}}^{(i)}; \theta_0, \theta_{\text{Ta}}) - L_{\text{Ta}}^{(i)} \right)^2.
        \end{equation}

@@

\begin{figure}[ht!]
    \includegraphics[width=\textwidth]{./project3/tikz/mtl.pdf}
    \caption{Multi-task learning framework for VA contracts}
    \label{fig3:mtl}
\end{figure}
